---
title: "Renamed Generic for Privacy"
#date: `r format(Sys.time(), "%d %B %Y")`
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    logo: ultraicon.jpg
    favicon: ultraicon.jpg
---

<style>.main-container { max-width: 1200px; margin-left: 0; margin-right: auto; }</style>

<!-- Pick a THEME keyword above from https://rstudio.github.io/shinythemes/ 
     My faves are spacelab (blue), united (purple), lumen and readable (white), --> 

```{r configuration}

filepath1 <- "/Users/name/Documents/generic/DataTable1.csv"
filepath2 <- "/Users/name/Documents/generic/DataTable2.csv"
filepath3 <- "/Users/name/Documents/generic/DataTable3.csv"
filepath4 <- "/Users/name/Documents/generic/DataTable4.csv"
filepath5 <- "/Users/name/Documents/generic/ColumnA.csv"

missing.threshold <- 50      # Raise a warning when more than X% of a feature is missing
outlier.threshold <- .3      # Raise a warning when more than X% of a feature are outliers
zero.threshold    <- .8      # Raise a warning when more than X% of a feature is zeroes
unique.threshold  <- 15      # Raise a warning when a categorical variable has more than X groups ("high cardinality")
p.threshold       <- 0.05    # Raise a warning when statistical tests reveal significance at this alpha level

# Set this to 0.01 or similar small number if dataset is larger (n > 100k)
sf                <- 1    # Sampling fraction for computationally complex visualizations

### (OPTIONAL) SET UP DATA TYPE DEFINITIONS & KEY BUSINESS VARIABLES EXTERNALLY
# source(paste0(filepath, "data-type-definitions.R"))

```



``````{r global-options, include=FALSE}
# This section suppresses all code and errors so only charts, graphs, and tables are visible. 
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE)

########## LOAD PACKAGES: Add your extra packages to the list. Common profiling packages are listed already.
   if (!require("pacman")) install.packages("pacman")
   library(pacman)
   pacman::p_load(ggplot2, dplyr, readr, tidyr, DT, knitr, lubridate, sparkline, flextable, openair, skimr,
                  magrittr, purrr, tibble, data.table, stringr, stringi, htmltools, janitor, ggcorrplot, tidyr,
                  cowplot, vroom, dlookr, visdat, DataExplorer, inspectdf, ggExtra, xray, GGally)
   
#############################################################################################################################
# Load common regular expressions (e.g. formats of URLs and Emails)
source("https://raw.githubusercontent.com/NicoleRadziwill/R-Functions/master/regexeR.R")
   
# Load supplemental profiling functions
source("https://raw.githubusercontent.com/NicoleRadziwill/R-Functions/master/profiling.R")
   
```


```{r load-clean}
# This section prepares a **data frame** named **xdata** that will be the subject of the deep profiling.

######### LOAD DATA (or sample of data) TO PROFILE ###############################################
data1 <- readr::read_csv(paste0(filepath1)) %>% janitor::clean_names()
DataTable1 <- data1  # Create container for manipulated data (xdata) based on raw data (data) that is ready to prof
data2 <- readr::read_csv(paste0(filepath2)) %>% janitor::clean_names()
DataTable2 <- data2  # Create container for manipulated data (xdata) based on raw data (data) that is ready to prof
data3 <- readr::read_csv(paste0(filepath3)) %>% janitor::clean_names()
DataTable3 <- data3  # Create container for manipulated data (xdata) based on raw data (data) that is ready to prof
data4 <- readr::read_csv(paste0(filepath4)) %>% janitor::clean_names()
DataTable4 <- data4  # Create container for manipulated data (xdata) based on raw data (data) that is ready to prof
data5 <- readr::read_csv(paste0(filepath5)) %>% janitor::clean_names()
ColumnA <- data5  # Create container for manipulated data (xdata) based on raw data (data) that is ready to prof
```


Sidebar {.sidebar data-width=550}
================================

### Executive Summary
```{r executive-summary}
htmltools::includeMarkdown("ExecutiveSummary.md")
```



###Dataset Level
===================================== 

Column {.tabset}
-------------------------------------

### DataTable 1
```{r dataset-summary-skim, results='asis'}
skimr::skim(DataTable1)
```

### DataTable 2
```{r dataset2-summary-skim, results='asis'}
skimr::skim(DataTable2)
# Include R code to generate one table, chart, or plot

```


### DataTable 3
```{r dataset3-summary-skim, results='asis'}
skimr::skim(DataTable3)
# Include R code to generate one table, chart, or plot

```

### DataTable 4
```{r dataset4-summary-skim, results='asis'}
skimr::skim(DataTable4)

```

### All DataTable Column A data
```{r dataset5-summary-skim, results='asis'}
skimr::skim(ColumnA)

```



### DataTable 1-4 Table
```{r dataset-summary-1}
# Prepare Data
DataTable1 %>% DataExplorer::introduce() -> values

   values$pct_missing_cells <- (values$total_missing_values/values$total_observations)*100
   variables <- c(names(DataExplorer::introduce(DataTable1)),"pct_missing_cells")

# Put info in right format for printing table
   all.values <- values %>% data.table::transpose()
   overall.df <- data.frame(cbind(variables,all.values))
   names(overall.df) <- c("Variable","Value")
   overall.df$Description <- c("Number of Rows/Observations","Number of Columns/Features","Categorical Variables",
                      "Quantitative Variables","Missing Columns/Features","Missing Cells (#)",
                      "Complete Rows/Observations","Total Cells","Memory Usage (KB)","Missing Cells (%)")

   # OPTIONAL: If you run this section and want to REORDER the columns for clearer communication, reorder them here:
   overall.df$Order <- c(1,3,5,6,4,7,2,9,10,8)

# Call out missing column names in the table footnote:
  
   
   # Create and display table:
   overall.df %>% arrange(Order) %>% select(Description,Value) %>% regulartable() %>% 
      autofit() %>% colformat_num(digits=0, big.mark=",") 
   
```


### DataTable 1-4 Avg Column A Table
```{r dataset-summary-2}
# Prepare Data
ColumnA %>% DataExplorer::introduce() -> values

   values$pct_missing_cells <- (values$total_missing_values/values$total_observations)*100
   variables <- c(names(DataExplorer::introduce(ColumnA)),"pct_missing_cells")

# Put info in right format for printing table
   all.values <- values %>% data.table::transpose()
   overall.df <- data.frame(cbind(variables,all.values))
   names(overall.df) <- c("Variable","Value")
   overall.df$Description <- c("Number of Rows/Observations","Number of Columns/Features","Categorical Variables",
                      "Quantitative Variables","Missing Columns/Features","Missing Cells (#)",
                      "Complete Rows/Observations","Total Cells","Memory Usage (KB)","Missing Cells (%)")

   # OPTIONAL: If you run this section and want to REORDER the columns for clearer communication, reorder them here:
   overall.df$Order <- c(1,3,5,6,4,7,2,9,10,8)

# Call out missing column names in the table footnote:
  
   
   # Create and display table:
   overall.df %>% arrange(Order) %>% select(Description,Value) %>% regulartable() %>% 
      autofit() %>% colformat_num(digits=0, big.mark=",") 
   

```





### DataTable 1 plot 
```{r dataset-summary-plot}

DataTable1 %>% DataExplorer::plot_intro()
```


### Column A plot 
```{r dataset-summary-plot2}

ColumnA %>% DataExplorer::plot_intro()

```


### Memory Usage DataTable
```{r memory-usage}
DataTable1 %>% inspectdf::inspect_mem() %>% arrange(desc(bytes)) %>% top_n(10) %>% regulartable() %>% autofit()

```


### Memory Usage Column A
```{r memory-usage-2}
ColumnA %>% inspectdf::inspect_mem() %>% arrange(desc(bytes)) %>% top_n(10) %>% regulartable() %>% autofit()

```

Summary 
===================================== 

Column {.tabset}
-------------------------------------

### Coverage DataTable
```{r coverage}
DataTable1 %>% visdat::vis_dat(warn_large_data = FALSE) 

```

### Coverage Column A
```{r coverage-2}
ColumnA %>% visdat::vis_dat(warn_large_data = FALSE) 

```

### All Numeric DataTable
```{r basic-profile-numeric}
DataTable1 %>% select_if(is.numeric) %>% dlookr::diagnose_numeric() -> left.df
DataTable1 %>% select_if(is.numeric) %>% inspectdf::inspect_num() ->   right.df

sparkify <- full_join(left.df, right.df) %>% 
  select(variables, min, Q1, median, mean, sd, Q3, max, zero, minus, outlier, hist) %>%
  rename(num_outliers=outlier) %>% mutate_if(is.numeric, round, digits=3)

  hist_sparks <- sparkify$hist %>% purrr::map( function(x) { 
    as.character(htmltools::as.tags(sparkline(x$prop)))  })
    sparkify$hist_sparks <- hist_sparks
  
  sparkify %>% select(-hist) %>% 
    datatable(rownames = FALSE, caption = htmltools::tags$caption(
       style = 'caption-side: top; text-align: left; font-size: 24px;',
       'NUMERIC ELEMENTS'),
       options= list(
         columnDefs=list(list(visible=FALSE, targets=c(c(10)))),
         fnDrawCallback=htmlwidgets::JS('function(){HTMLWidgets.staticRender();}')
       )
    ) %>% sparkline::spk_add_deps()

```


### All Numeric Column A
```{r basic-profile-numeric-2}
ColumnA %>% select_if(is.numeric) %>% dlookr::diagnose_numeric() -> left.df
ColumnA %>% select_if(is.numeric) %>% inspectdf::inspect_num() ->   right.df

sparkify <- full_join(left.df, right.df) %>% 
  select(variables, min, Q1, median, mean, sd, Q3, max, zero, minus, outlier, hist) %>%
  rename(num_outliers=outlier) %>% mutate_if(is.numeric, round, digits=3)

  hist_sparks <- sparkify$hist %>% purrr::map( function(x) { 
    as.character(htmltools::as.tags(sparkline(x$prop)))  })
    sparkify$hist_sparks <- hist_sparks
  
  sparkify %>% select(-hist) %>% 
    datatable(rownames = FALSE, caption = htmltools::tags$caption(
       style = 'caption-side: top; text-align: left; font-size: 24px;',
       'NUMERIC ELEMENTS'),
       options= list(
         columnDefs=list(list(visible=FALSE, targets=c(c(10)))),
         fnDrawCallback=htmlwidgets::JS('function(){HTMLWidgets.staticRender();}')
       )
    ) %>% sparkline::spk_add_deps()
  
```


Distributions
===================================== 

Column {.tabset}
-------------------------------------

### All Numeric DataTable
```{r distrib-quant}
DataTable1 %>% select_if(is.numeric) %>% DataExplorer::plot_histogram(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### All Numeric Column A
```{r distrib-quant-2}
ColumnA %>% select_if(is.numeric) %>% DataExplorer::plot_histogram(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### Tests for Normality DataTable
```{r distrib-qq}
DataTable1 %>% select_if(is.numeric) %>% DataExplorer::plot_qq(ncol=3, theme_config=list("text"=element_text(size=8)))

```

### Tests for Normality
```{r distrib-qq-2}
ColumnA %>% select_if(is.numeric) %>% DataExplorer::plot_qq(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### Log Distributions DataTable
```{r distrib-log}
DataTable1 %>% select_if(is.numeric) %>% 
  mutate_all(~log1p(.)) %>% DataExplorer::plot_histogram(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### Log Distributions Column A
```{r distrib-log-2}
ColumnA %>% select_if(is.numeric) %>% 
  mutate_all(~log1p(.)) %>% DataExplorer::plot_histogram(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### Tests for Lognormality DataTable
```{r distrib-log-qq}
DataTable1 %>% select_if(is.numeric) %>% 
  mutate_all(~log1p(.)) %>% DataExplorer::plot_qq(ncol=3, theme_config=list("text"=element_text(size=8)))
```

### Boxplots by Factors
```{r distrib-boxplots}
# This automatically ignores high cardinality categorical variables (more than 50 categories)
factorlist <- DataTable1 %>% select_if(is.factor) %>% colnames()

for(f in factorlist) {
   DataTable1 %>% DataExplorer::plot_boxplot(ncol=3, by=f, theme_config=list("text"=element_text(size=8)))
} 
```
  
Relationships and Correlations
=====================================

Column {.tabset}
-------------------------------------

### Scatterplots DataTable
```{r scatterplots}
DataTable1 %>% select_if(is.numeric) %>% ggpairs()
```

### Scatterplots Column A
```{r scatterplots-2}
ColumnA %>% select_if(is.numeric) %>% ggpairs()
```

### Marginal Plots DataTable
```{r marginals}
# Marginal plots are documented at https://deanattali.com/2015/03/29/ggExtra-r-package/ 

# CHOOSE THE QUANTITATIVE VARIABLES YOU WANT on the X and Y AXES MANUALLY. 
# I chose two pairs for this example: (length, years) and (length, appliance)

p <- ggplot(DataTable1, aes(x = "Column B[15,1]", y="ColumnB[15,1]")) + geom_point() + theme_bw() 

p + ggtitle("ColumnB VS ColumnC")

# Now display the plot you stored in the variable p:
ggMarginal(p, type="histogram")


p <- ggplot(DataTable1, aes(x="ColumnC total[15]", y="ColumnD total - crop[15]")) + geom_point() + theme_bw() 

p + ggtitle("ColumnC Total VS ColumnD Total")

ggMarginal(p, type="histogram")

```

### Correlation Plot DataTable
```{r corr-plot}
DataTable1 %>% select_if(is.numeric) %>% ggcorr(., nbreaks=5, palette="RdGy", label=TRUE, label_size=3, label_color="white")
```

### Correlation Plot Column A
```{r corr-plot-2}
ColumnA %>% select_if(is.numeric) %>% ggcorr(., nbreaks=5, palette="RdGy", label=TRUE, label_size=3, label_color="white")
```

Data Quality Issues
===================================== 

Column {.tabset}
-------------------------------------

### Anomalies DataTable
```{r anomalies}
DataTable1 %>% xray::anomalies() -> anomalous
anomalous$variables %>% select(-q,type) %>% arrange(desc(anomalous_percent)) %>% regulartable() %>% autofit()
```

### Anomalies Column A
```{r anomalies-2}
ColumnA %>% xray::anomalies() -> anomalous
anomalous$variables %>% select(-q,type) %>% arrange(desc(anomalous_percent)) %>% regulartable() %>% autofit()
```

### Missing Data DataTable
```{r missing-data-table-1}
DataTable1 %>% dlookr::diagnose() %>% 
   arrange(desc(missing_percent)) %>% mutate_if(is.numeric, round, digits=3) %>% 
   DT::datatable(rownames = FALSE, caption = htmltools::tags$caption(
   style = 'caption-side: top; text-align: left; font-size: 24px;',
   'MISSING DATA (Summary)'))
```

### Missing Data Column A
```{r missing-data-table-1-2}
ColumnA %>% dlookr::diagnose() %>% 
   arrange(desc(missing_percent)) %>% mutate_if(is.numeric, round, digits=3) %>% 
   DT::datatable(rownames = FALSE, caption = htmltools::tags$caption(
   style = 'caption-side: top; text-align: left; font-size: 24px;',
   'MISSING DATA (Summary)'))
```

### Missing Data DataTable
```{r missing-data-table-2}
# This colors all rows that are "good" (missing percent < threshold set in configuration chunk)
DataTable1 %>% dlookr::diagnose() %>% arrange(missing_percent) %>% regulartable() %>% autofit() %>% 
    bg(i=~missing_percent<missing.threshold, bg="#cceecc", part="body")
```


### Missing Data Column A
```{r missing-data-table-2-2}
# This colors all rows that are "good" (missing percent < threshold set in configuration chunk)
ColumnA %>% dlookr::diagnose() %>% arrange(missing_percent) %>% regulartable() %>% autofit() %>% 
    bg(i=~missing_percent<missing.threshold, bg="#cceecc", part="body")
```


### Missing Data DataTable
```{r missing-data-visdat}
# Include R code to generate one table, chart, or plot
DataTable1 %>% visdat::vis_dat(warn_large_data=FALSE, sort_type=F)

# Add "+ theme(axis.text.x=element_blank())" to the above line of code to remove variable names, if there are too many
```

### Missing Data Column A
```{r missing-data-visdat-2}
# Include R code to generate one table, chart, or plot
ColumnA %>% visdat::vis_dat(warn_large_data=FALSE, sort_type=F)

# Add "+ theme(axis.text.x=element_blank())" to the above line of code to remove variable names, if there are too many
```

### Missing Data DataTable
```{r missing-data-dataexplorer}
# Include R code to generate one table, chart, or plot
DataTable1 %>% DataExplorer::plot_missing()
```

### Missing Data Column A
```{r missing-data-dataexplorer-2}
# Include R code to generate one table, chart, or plot
ColumnA %>% DataExplorer::plot_missing()
```

### Imbalanced Classes DataTable
```{r imbalanced-1-1}
DataTable1 %>% mutate_if(is.factor, as.character) %>% inspect_imb()
```

### Imbalanced Classes Column A
```{r imbalanced-1-2}
ColumnA %>% mutate_if(is.factor, as.character) %>% inspect_imb()
```

### Imbalanced Classes Plot DataTable
```{r imbalanced-2-1}
DataTable1 %>% mutate_if(is.factor, as.character) %>% inspect_imb() %>% show_plot()
```

### Imbalanced Classes Plot Column A
```{r imbalanced-2-2}
ColumnA %>% mutate_if(is.factor, as.character) %>% inspect_imb() %>% show_plot()
```

### Potential Outliers DataTable
```{r outliers, echo=FALSE, warning=FALSE, message=FALSE}
DataTable1 %>% select_if(is.numeric) %>% dlookr::diagnose_outlier() -> outliers.df
DataTable1 %>% select_if(is.numeric) %>% dlookr::diagnose_numeric() -> outlierdetails.df

inner_join(outliers.df, outlierdetails.df, "variables") %>% 
  select(-with_mean,-without_mean,-outliers_cnt,-outliers_mean) %>%
  arrange(desc(outliers_ratio)) %>% rename(num_outliers=outlier) %>% regulartable() %>% autofit() %>% 
  bg(i=~outliers_ratio>5, bg="#eecccc", part="body")

```

### Potential Outliers Column A
```{r outliers-2, echo=FALSE, warning=FALSE, message=FALSE}
ColumnA %>% select_if(is.numeric) %>% dlookr::diagnose_outlier() -> outliers.df
ColumnA %>% select_if(is.numeric) %>% dlookr::diagnose_numeric() -> outlierdetails.df

inner_join(outliers.df, outlierdetails.df, "variables") %>% 
  select(-with_mean,-without_mean,-outliers_cnt,-outliers_mean) %>%
  arrange(desc(outliers_ratio)) %>% rename(num_outliers=outlier) %>% regulartable() %>% autofit() %>% 
  bg(i=~outliers_ratio>5, bg="#eecccc", part="body")

```

